---
title: "HW02_Shot_Charts"
author: "Daniel Vo"
date: "3/4/2018"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.path = "../images/")
```

```{R}
library(dplyr)
library(ggplot2)
dt <- read.csv(file = "../data/shots-data.csv")
group_by(dt, name)


dt1 <- arrange(summarise(
  group_by(dt, name),
  total = length(shot_made_flag)), desc(total))

dt <- mutate(dt, made = as.numeric(shot_made_flag=="made shot"))


dt2 <- summarise(
  group_by(dt, name),
  total = length(shot_made_flag),
  made = sum(made)
)

dt2 <- mutate(dt2, perc.made = 100*made/total)

dt3 <- summarise(
  group_by(dt, shot_distance),
  made_shot_prop = mean(as.numeric(shot_made_flag=="made shot"))
)

ggplot(data = dt3, aes(x = shot_distance, y = made_shot_prop))+
  geom_point()+
  theme_minimal()

filter(dt3, made_shot_prop>=0.5)$shot_distance
```

#Comment on the Scatter Plot

What do you observe?
- Downward trend in probability as we go from distance 0 to distance 3 or 4. Probability is considerably similar between distance 3-4 to distance 33-35. From distance 33-35 and above, probability of making the shot is zero. There's a outline at distance 51, which is caused by the only data point at this distance, and that was a made shot by Stephen Curry

Can you confirm that the shorter the distance, the more effective the shots?
- We can do that only for the first 3 distance points. But we cannot confirm this once it is between 3-4 to 33-35 ft. away

Can you guesstimate a distance threshold beyond which the chance of making a
successful shot is basically null?
- 34 ft.

What distances tend to have a percentage (of making a shot) of 50% or more?
- The following distances: 0  1  2 12 16 18 21 30 51

#Total number of shots by minute of occurrence
```{r}

dt4 <- summarise(
  group_by(dt, minute, name),
  number_shot=length(shot_made_flag)
)

ggplot(data = dt4, aes(x = minute, y = number_shot))+
  xlab("Minutes of Occurance")+
  ylab("Total Number of Shots")+
  geom_point()+
  scale_x_continuous(breaks = c(12,24,36,48))+
  geom_path() +
  theme_minimal()+
  geom_rect(xmin=0, xmax=12, ymin=0, ymax=60, alpha=0.01)+
  geom_rect(xmin=24, xmax=36, ymin=0, ymax=60, alpha=0.01)+
  facet_wrap( ~name)
```









